\documentclass[11pt, final]{article}
\usepackage{tar}

\begin{document}

    \reporttitle{Trustees Annual Report\\01 Apr 2021 -- 31 Mar 2022}

    \section{Reference and Administration Details}
    \begin{tabular}{l l}
        \textbf{Charity Name:} & The UK Python Association \\
        \textbf{Charity Number:} & 1173471 \\
        \textbf{Principal Address:} & c/o Acconomy \\
	& Arena Business Centre \\
	& Holyrood Close \\
	& Poole BH17 7FJ\\
    \end{tabular}

        \subsection{Trustees}
        \begin{tabular}{l l}
    	        Tania Allard & Kristian Glass\\
                Ann Barr & Gail Ollis\\
                Owen Campbell & Vincent Prytherch\\
        \end{tabular}

    \section{Objectives and Activities}
	The objectives of the UKPA are:
	\begin{enumerate}
		\item To advance education for the public benefit in the use and understanding of the Python programming language within the UK by:
		\begin{enumerate}
			\item Organising, presenting and promoting Python related conferences, meetings and events at venues within the UK,
			\item Supporting and promoting Python related projects and events organised by UKPA members, and,
			\item Supporting UKPA members wishing to attend Python related conferences, meetings and events.
		\end{enumerate}
		\item To advance education for the public benefit in the use and understanding of the Python programming language worldwide by supporting and promoting overseas Python related conferences, meetings and events.
	\end{enumerate}

    The primary activity of the UKPA is to organise and run the annual PyCon UK conference.

    \section{Structure, Governance and Management}

        \subsection{Governing Document}
        The UKPA's governing document is its constitution, the current version of which is available at https://github.com/PyconUK/ukpa-constitution/releases/latest.

        \subsection{UKPA Members}
        The UKPA membership is the electoral body to which the trustees are accountable.
		There are two classes of membership:

		\begin{enumerate}
			\item Members: have the full rights and obligations described in the UKPA constitution, including the right to vote on members decisions.
			\item Associate Members: non-voting class of membership as described in the UKPA constitution.
		\end{enumerate}

        \subsection{Trustee Appointment}
		At the AGM in 2021, Cecilia Liao retired as a trustee.

	    \subsection{Risk and Internal Control}
        The trustees have identified the major risks to which they believe the UKPA is exposed. These are:

          \subsubsection{Reduction or Loss of Members}
            If there were a reduction in membership of the UKPA then there would have to be a contraction, consolidation or closure of its activities.

            \subsubsection{Injury to Members, Conference Attendees or Trustees}
            The UKPA requires insurance to cover this potential risk and the trustees intend to put that insurance in place once the UKPA has sufficient funds to cover the cost of the premium.

            \subsubsection{Reduction or Loss of Volunteers}
            The UKPA is totally reliant upon volunteers to run and administer the activities of the UKPA. If there were a reduction in the number of volunteers to an unacceptable level, then there would have to be a contraction, consolidation or closure of activities.

    \section{Achievements and Performance}
    	As a result of the ongoing COVID19 pandemic, the trustees decided to cancel the 2021 PyCon UK event and there was no other significant activity during the course of the year.
    \section{Financial Review}

        \subsection{Reserves Policy}
		The UKPA has undertaken a review of its potential liabilities in the face of foreseeable risks and determined that a reasonable sum to hold in reserve is that required to cover a year's operational expenditure plus some contingency for unforeseen costs: \pounds10K

        At the end of March 2022, the UKPA held reserves of \pounds TODO.

        All funds raised from previous PyCon UK conferences are currently held by PyCon UK Society Ltd (PUKSL). The intention is that these funds will be transferred to the new subsidiary trading company  and PUKSL will be closed.

        \subsection{Investment Policy}
        The UKPA has adopted a low risk strategy and all funds are held in cash using only mainstream banks or building societies.

    \section{Declaration}
    The trustees declare that they have approved the trustees report above.

    
    Signed on behalf of the charity's trustees:
    
    \begin{tabular}{l l}
        \textbf{Signature:}\vspace{3cm}\\
        \textbf{Date:} & TODO September 2022\vspace{1cm}\\
        \textbf{Full Name:} & Owen Campbell \\
    \end{tabular}

\end{document}
