\documentclass[11pt, final]{article}
\usepackage{tar}

\begin{document}

\reporttitle{Trustees Annual Report\\01 Apr 2023 -- 31 Mar 2024}

\section{Reference and Administration Details}
\begin{tabular}{l l}
	\textbf{Charity Name:}      & The UK Python Association \\
	\textbf{Charity Number:}    & 1173471                   \\
	\textbf{Principal Address:} & c/o Acconomy              \\
	                            & Arena Business Centre     \\
	                            & Holyrood Close            \\
	                            & Poole BH17 7FJ            \\
\end{tabular}

\subsection{Trustees}
\begin{tabular}{l l}
	Owen Campbell  & Daniele Procida \\
	Kristian Glass & Rebecca Smith \\
\end{tabular}

\section{Objectives and Activities}
The objectives of the UKPA are:
\begin{enumerate}
	\item To advance education for the public benefit in the use and understanding of the Python programming language within the UK by:
	      \begin{enumerate}
		      \item Organising, presenting and promoting Python related conferences, meetings and events at venues within the UK,
		      \item Supporting and promoting Python related projects and events organised by UKPA members, and,
		      \item Supporting UKPA members wishing to attend Python related conferences, meetings and events.
	      \end{enumerate}
	\item To advance education for the public benefit in the use and understanding of the Python programming language worldwide by supporting and promoting overseas Python related conferences, meetings and events.
\end{enumerate}

The primary activity of the UKPA is to organise and run the annual PyCon UK conference.

\section{Structure, Governance and Management}

\subsection{Governing Document}
The UKPA's governing document is its constitution, the current version of which is available at https://github.com/PyconUK/ukpa-constitution/releases/latest.

\subsection{UKPA Members}
The UKPA membership is the electoral body to which the trustees are accountable.
There are two classes of membership:

\begin{enumerate}
	\item Members: have the full rights and obligations described in the UKPA constitution, including the right to vote on members decisions.
	\item Associate Members: non-voting class of membership as described in the UKPA constitution.
\end{enumerate}

\subsection{Trustee Appointment}
At the AGM held on 24-Sep-2023, Vincent Knight retired as a trustee in accordance with section 13.1.1 of the UKPA's constitution.

Rebecca Smith also retired as a trustee in accordance with sections 13.1.4 and 13.1.5 of the constitution.

Vincent Knight and Rebecca Smith were elected as trustees for a further term in accordance with section 13.1.4 of the constitution.

On 04-Oct-2023, Vincent Knight resigned as a trustee.

By a resolution dated 10-Oct-2023, Daniele Procida was appointed as a trustee of the UKPA in accordance with clause 13.1.4 of the constitution
\subsection{Risk and Internal Control}
The trustees have identified the major risks to which they believe the UKPA is exposed. These are:

\subsubsection{Reduction or Loss of Members}
If there were a reduction in membership of the UKPA then there would have to be a contraction, consolidation or closure of its activities.


\subsubsection{Reduction or Loss of Volunteers}
The UKPA is totally reliant upon volunteers to run and administer the activities of the UKPA. If there were a reduction in the number of volunteers to an unacceptable level, then there would have to be a contraction, consolidation or closure of activities.

\section{Achievements and Performance}
The UKPA staged DjangoCon Europe which took place in Edinburgh from 29th May to 2nd June 2023.

PyCon UK 2023 was held at Cardiff City Hall from 22nd to 25th September 2023.

The UKPA provided financial support to DjangoCon Africa which took place in Zanzibar from 6th to 11th November 2023.

\section{Financial Review}

\subsection{Reserves Policy}
The UKPA has undertaken a review of its potential liabilities in the face of foreseeable risks and determined that a reasonable sum to hold in reserve is that required to cover a year's operational expenditure plus some contingency for unforeseen costs: \pounds10K

At the end of March 2024, the UKPA held reserves of \pounds 9093.94.

All funds raised from previous PyCon UK conferences are currently held by PyCon UK Society Ltd (PUKSL). 

Funds from the 2023 PyCon UK conference are held by the wholly owned subsidiary trading company, UKPA Trading Ltd (UKPATL). The intention is that funds held by PUKSL will be transferred to UKPATL and PUKSL will be closed.

\subsection{Investment Policy}
The UKPA has adopted a low risk strategy and all funds are held in cash using only mainstream banks or building societies.

\section{Declaration}
The trustees declare that they have approved the trustees report above.


Signed on behalf of the charity's trustees:

\begin{tabular}{l l}
	\textbf{Signature:}\vspace{3cm}                       \\
	\textbf{Date:}      & TODO\vspace{1cm} \\
	\textbf{Full Name:} & Owen Campbell                   \\
\end{tabular}

\end{document}
